Malacology: A Programmable Storage System

### 2016-10-20 paper/paper.tex
tweaks to abstract

\begin{abstract}
Storage systems are caught between rapidly changing data processing
applications and the increasing speed of storage devices. This puts tremendous
pressure on storage systems to support rapid evolution both in terms of their
interfaces and their performance. But adapting storage systems can be difficult
because unprincipled changes might jeopardize years of code-hardening and
performance optimization efforts that were necessary for users to entrust their
data to the storage system.  We introduce  Malacology, a prototype programmable
storage system to explore how existing abstractions of common services found in
storage systems can be leveraged to address new data processing systems and the
increasing speed of storage devices. This approach allows a large degree of
flexibility for storage systems to evolve without sacrificing the robustness of
their code-hardened subsystems.  We illustrate the advantages and challenges of
programmability by composing existing primitives into two new higher-level
services: a file system metadata load balancer and a high-performance
distributed shared-log that leverages flash devices. The evaluation
demonstrates that our services inherit desirable qualities of the back-end
storage system, including the ability to balance load, efficiently propagate
cluster metadata, recover from failure, and to make trade-offs for
latency/throughput using leases.
\end{abstract}

>>>>

\begin{abstract}
Storage systems are caught between rapidly changing data processing
applications and the increasing speed of storage devices. This puts tremendous
pressure on storage systems to support rapid evolution both in terms of their
interfaces and their performance. But adapting storage systems can be difficult
because unprincipled changes might jeopardize years of code-hardening and
performance optimization efforts that were necessary for users to entrust their
data to the storage system.  We introduce  Malacology, a prototype programmable
storage system, to explore how existing abstractions of common storage system services 
%found in
%storage systems 
can be leveraged to 
%address 
adapt to the needs of
new data processing systems and the
increasing speed of storage devices. This approach allows a large degree of
flexibility for storage systems to evolve without sacrificing the robustness of
their code-hardened subsystems.  We illustrate the advantages and challenges of
programmability by composing existing primitives into two new higher-level
services: a file system metadata load balancer and a high-performance
distributed shared-log that leverages flash devices. The evaluation
demonstrates that our services inherit desirable qualities of the back-end
storage system, including the ability to balance load, efficiently propagate
cluster metadata, recover from failure, and to navigate trade-offs between
latency and throughput using leases.
\end{abstract}
